

\newcommand{\nomunit}[1]{%
\renewcommand{\nomentryend}{\hspace*{\fill}#1}}


% first letter a is for Greek Symbols

\nomenclature[a,01]{$\alpha$}{Albedo of ground}  
\nomenclature[a,02]{$\gamma$}{Inclination angle of PV cell, $\gamma \in[0^{\mathrm{o}},90^{\mathrm{o}}]$}  
\nomenclature[a,03]{$\Delta_1$}{Gain of adding the $1^{\mathrm{st}}$ PV cell, cf. (\ref{Delta_1})}
\nomenclature[a,04]{$\Delta_n$}{Gain of adding the $n^{\mathrm{th}}$ PV cell, $n\in\{2, ..., N\}$, cf. (\ref{Delta_n})}
\nomenclature[a,05]{$\delta_d$}{Declination angle, cf. (\ref{delta})}
\nomenclature[a,06]{$\zeta_t$}{Zenith angle, cf. (\ref{zenith})}
\nomenclature[a,07]{$\eta$}{Energy conversion efficiency of PV cell}
\nomenclature[a,08]{$\theta$}{Orientation angle of PV cell, $\theta\in[-90^{\mathrm{o}},90^{\mathrm{o}}]$}
\nomenclature[a,09]{$\theta^*$}{Optimal orientation angle of PV cell, $\theta^*\in[-90^{\mathrm{o}},90^{\mathrm{o}}]$}
\nomenclature[a,10]{$\theta_n$}{Orientation angle of PV cell $n$, $\theta_n\in[-90^{\mathrm{o}},90^{\mathrm{o}}]$} 
\nomenclature[a,11]{$\theta_n^*$}{Optimal orientation angle of PV cell $n$, $\theta_n^*\in[-90^{\mathrm{o}},90^{\mathrm{o}}]$} 
\nomenclature[a,12]{$\lambda(t)$}{Density parameter of Poisson distributed random variable at time step $t$, cf. (\ref{P})}
\nomenclature[a,13]{$\mu$}{Precision of the discretization of the energy values/ battery states}
\nomenclature[a,14]{$\rho$}{Resistivity of the distribution line } %\nomunit{[$\mathrm{\Omega}$ m]}
\nomenclature[a,15]{$\tau$}{Duration of one time step } %  \nomunit{[s]}
\nomenclature[a,16]{$\omega_t$}{Hour angle, cf. Figure \ref{hour_angle_graph}}



% first letter b is for Roman symbols capital letter


\nomenclature[b,01]{$A$}{Total surface area of $N$ PV cells}% \nomunit{[$\mathrm{m}^2$]} 
\nomenclature[b,02]{$A_c$}{Cross-sectional area of the distribution line}% \nomunit{[$\mathrm{m}^2$]}
\nomenclature[b,03]{$A_t$}{Anisotropy index at time step $t$, cf. (\ref{At})}  
\nomenclature[b,04]{$AOI_{\theta}(t)$}{Angle of incidence of a PV cell deployed with orientation angle $\theta$ at time step $t$, cf. (\ref{allgemein_AOI})}  
\nomenclature[b,05]{$B$}{Number of BSs in the square area of $l^2$ square meters, cf. Figure \ref{fig:1}}  
\nomenclature[b,11]{$BS_i$}{BS with index $i$}  
\nomenclature[b,12]{$C$}{Power loss coefficient per $l$ meters of distribution line}% \nomunit{[$\mathrm{\Omega}$]}  
\nomenclature[b,13]{$C(t)$}{Energy consumption of the BS at time step $t$, cf. Figures \ref{constant_allgemein} - \ref{residential_allgemein}}% \nomunit{[J]} 
\nomenclature[b,14]{$C_{\mathrm{bus}}(t)$}{Business-area traffic load profile at time step $t$, cf. Figure \ref{all_consumption_profiles}}  
\nomenclature[b,15]{$C_{\mathrm{con}}(t)$}{Constant traffic load profile at time step $t$, cf. Figure \ref{all_consumption_profiles}}  
\nomenclature[b,21]{$C_{\mathrm{res}}(t)$}{Residential-area traffic load profile at time step $t$, cf. Figure \ref{all_consumption_profiles}} 
\nomenclature[b,22]{$DHI_t$}{Diffuse horizontal irradiance at time step $t$, obtained from PVGIS \cite{PVGIS}}  
\nomenclature[b,23]{$DNI_t$}{Direct normal irradiance at time step $t$, obtained from PVGIS \cite{PVGIS}}  
\nomenclature[b,24]{$E$}{Set of edges in the graph/cellular network, cf. (\ref{V_and_E})} 
\nomenclature[b,25]{$E_{\mathrm{con}}$}{Solar constant set at $1367\frac{\mathrm{W}}{\mathrm{m}^2}$ \cite{Solar_Cell_declination_inclination_angle}} 
\nomenclature[b,26]{$E_d$}{Extraterrestrial radiation on day $d$, cf. (\ref{extra})} 
\nomenclature[b,31]{$G(t)$}{Energy generation of the PV cell/cells at time step $t$}  
\nomenclature[b,32]{$G^{\text{original}}_{\theta,N}(t)$}{Energy generated by one PV cell installed with $\theta$ ($N$ is the total number of PV cells) at time step $t$, cf. (\ref{normalization})}  
\nomenclature[b,330]{$G_{\theta,N}(t)$}{Normalized energy generated by one PV cell installed with $\theta$ ($N$ is the total number of PV cells) at time step $t$, cf. (\ref{norma})} 
\nomenclature[b,335]{$\tilde{G}_{\theta,1}(t)$}{Closest multiple of $\mu$ from $G_{\theta,1}(t)$} 
\nomenclature[b,34]{$G_{(\theta_1, ..., \theta_N)}(t)$}{Normalized total energy generated by $N$ PV cells installed with $\theta_1, ....,\theta_N$ at time step $t$, cf. (\ref{nor})}   
\nomenclature[b,35]{$GHI_t$}{Global horizontal irradiance at time step $t$, obtained from PVGIS \cite{PVGIS}}   
\nomenclature[b,41]{$I_{\theta}(t)$}{Irradiance on PV cell installed with orientation angle $\theta$ at time step $t$, cf. (\ref{I1})} 
\nomenclature[b,42]{$I_{b_\theta}(t)$}{Direct-beam irradiance at time step $t$, cf. (\ref{I4})} 
\nomenclature[b,43]{$I_{d_\theta}(t)$}{Sky-diffuse irradiance at time step $t$, cf. (\ref{reindl})} 
\nomenclature[b,44]{$I_{g}(t)$}{Ground-reflected irradiance at time step $t$, cf. (\ref{I3})} 
\nomenclature[b,45]{$I_{\mathrm{ele}}$}{Electric current traveling through the distribution line}% \nomunit{[A]}
\nomenclature[b,51]{$L$}{Number of loops in simulation algorithm}
\nomenclature[b,52]{$M$}{Total normalized renewable power received at the deficit BSs during the two time steps}% \nomunit{[W]}
\nomenclature[b,53]{$N$}{Number of PV cells at the BS}  
\nomenclature[b,54]{$P_{\mathrm{loss}}$}{Power loss in the transmission due to resistive heating, cf. (\ref{loss})}% \nomunit{[W]}
\nomenclature[b,55]{$S_{\max}$}{Number of battery energy states, cf. (Algorithm \ref{mar} line: \ref{battery_stages})} 
\nomenclature[b,61]{$S_{\mathrm{Shift}}$}{New battery state after $\tilde{G}_{\theta,1}(t)$ is added and $c_{\mathrm{con}}$ is subtracted, cf. (Algorithm \ref{mar} line: \ref{she})} 
\nomenclature[b,62]{$S_{\mathrm{UE}}(\theta)$}{Number of UEs served per day by the BS, cf. (\ref{PPP})}  
\nomenclature[b,63]{$\overline{S_{\mathrm{UE}}}(\theta)$}{Average number of UEs served per day by the BS, cf. (\ref{PPP})}  
\nomenclature[b,64]{$T$}{Number of time steps per day}    
\nomenclature[b,65]{$V$}{Set of vertices in the graph/ cellular network, cf. (\ref{V_and_E})}  
\nomenclature[b,66]{$V_{\mathrm{ele}}$}{Electric potential in the distribution line}% \nomunit{[V]}


			

% first letter c is for Roman symbols small letter 
\nomenclature[c,001]{$a_\theta(t)$}{Available energy in the battery at the beginning of time step $t$, cf. (\ref{available})} %\nomunit{[J]}
\nomenclature[c,001]{$a_t$}{Part of $\cos(AOI_{\theta}(t))$ that is independent of $\theta$, cf. (\ref{a_t})} 
\nomenclature[c,001]{$b_t$}{Part of $\cos(AOI_{\theta}(t))$ that is multiplied by  $\sin(\theta)$, cf.  (\ref{b_t})} 
\nomenclature[c,011]{$b_\theta(t)$}{Stored energy in the battery at the end of time step $t$, cf. (\ref{bat})} %\nomunit{[J]}
\nomenclature[c,012]{$b_{\mathrm{begin}}$}{Amount of energy stored in the battery at time step $0$}  %\nomunit{[J]}
\nomenclature[c,013]{$b_{\mathrm{max}}$}{Battery capacity}  	%\nomunit{[J]}
\nomenclature[c,014]{$b_0$}{Power surplus value, $b_0\in \mathbb{R}^+$} %\nomunit{[W]}}
\nomenclature[c,015]{$b_1$}{Power deficit value, $b_1\in \mathbb{R}^-$} %\nomunit{[W]}}
\nomenclature[c,016]{$\hat{b}_0$}{Normalize power surplus value with respect to $\mathrm{max}\{b_0,\lvert b_1 \rvert\}$, cf. (\ref{normal})} %\nomunit{[W]}} %
\nomenclature[c,017]{$\hat{b}_1$}{Normalize power deficit value with respect to $\mathrm{max}\{b_0,\lvert b_1 \rvert\}$, cf. (\ref{normal})}  %\nomunit{[W]}
\nomenclature[c,021]{$c_\theta(t)$}{Load-dependent energy consumption of the BS at time step t, cf. (\ref{PPP3})} 		%\nomunit{[J]}									
\nomenclature[c,022]{$c_{\mathrm{con}}$}{Load-independent part of the energy consumption at the BS in one time step}%\nomunit{[J]}
\nomenclature[c,023]{$c_i$}{Cluster allocation value of $BS_i$, $c_i\in\{0,1\}$}  
\nomenclature[c,024]{$c_t$}{Part of $\cos(AOI_{\theta}(t))$ that is multiplied by  $\cos(\theta)$, cf.  (\ref{c_t})}
\nomenclature[c,025]{$c_{\mathrm{UE}}$}{Average energy consumption of the BS to serve one UE during a time step}%	\nomunit{[J]}	 
\nomenclature[c,026]{$d$}{Day of the year with $1^{\mathrm{st}}$ of January is $d=1$} 
\nomenclature[c,031]{$d\big((i,j)\big)$}{Normalize Euclidean distance between $BS_i$ and $BS_j$ with respect to $l$ meters, cf. (\ref{equ_y})} 
\nomenclature[c,041]{$e$}{Edge $e$ in a graph}
\nomenclature[c,043]{$f^t\big((i,j)\big)$}{Power flow on the directed edge from $BS_i$ to $BS_j$ at time step $t$ or second power of the current flow on the directed edge from $BS_i$ to $BS_j$ at time step $t$}% \nomunit{[W]}
\nomenclature[c,044]{$\hat{f}^t\big((i,j)\big)$}{Normalize power flow value with respect to $\mathrm{max}\{b_0,\lvert b_1 \rvert\}$ on the directed edge from $BS_i$ to $BS_j$ at time step $t$, cf. (\ref{normal})}%\nomunit{[W/$\mathrm{A}^2$]}
\nomenclature[c,045]{$f(\theta_1, ..., \theta_N)$}{Normalized energy drawn from the grid, Optimization objective, cf. (\ref{optimization_objective})}
\nomenclature[c,046]{$l$}{Side length of the square in Fig \ref{fig:1}}% \nomunit{[m]} 
\nomenclature[c,047]{$lat$}{Latitude of location}  
\nomenclature[c,048]{$lon$}{Longitude of location}  
\nomenclature[c,049]{$l(t)$}{Number of UEs connected to the BS at time step $t$, cf.  (\ref{PPP1})} 
\nomenclature[c,060]{$n$}{Index of BS, $n\in\{1, ..., N\}$}      
\nomenclature[c,061]{$p_i^t$}{Surplus/Deficit power of $BS_i$ at time step $t$, cf. (\ref{p_values})}% \nomunit{[W]}
\nomenclature[c,062]{$q$}{Probability that two BSs are connected by a distribution line, $q \in [0,1]$} 
\nomenclature[c,063]{$s_\theta(t)$}{Number of served UEs by the BS at time step $t$, cf. (\ref{PPP2})} 
\nomenclature[c,064]{$t$}{Index of time step, $t\in\{1, ..., T\}$}   
\nomenclature[c,065]{$v$}{Vertex $v$ in a graph}


% first letter R is for superscript
\nomenclature[r,02]{$^*$}{Optimal value}  

% first letter S is for subscripts  
\nomenclature[s,01]{$_{\theta}$}{Parameter depends on the PV cell orientation angle $\theta$}
\nomenclature[s,02]{$_{d}$}{Parameter depends on the day of the year with $1^{\mathrm{st}}$ of January is $d=1$}  
\nomenclature[s,03]{$_{i}$}{Index of BS, $i\in\{1, ..., B\}$}
\nomenclature[s,04]{$_{j}$}{Index of BS, $j\in\{1, ..., B\}$}
\nomenclature[s,05]{$_n$}{Index of PV cell, $n\in\{1, ..., N\}$} 
\nomenclature[s,06]{$_t$}{Index of time step, $t\in\{1, ..., T\}$}  

  
 
                  







 %first letter Z is for Acronyms 

\nomenclature[z,02]{A*STAR}{Agency for Science, Technology and Research in Singapore}
\nomenclature[z,02]{BS}{Base station}
\nomenclature[z,02]{AC}{Alternating current}
\nomenclature[z,02]{DC}{Direct current}
\nomenclature[z,02]{MILPP}{Mixed-integer linear programming problem}
\nomenclature[z,02]{GIS}{Geographic information system}
\nomenclature[z,02]{PV}{Photovoltaic}
\nomenclature[z,02]{PVGIS}{Photovoltaic geographic information system}
\nomenclature[z,02]{SINR}{Signal-to-interference-plus-noise ratio}
\nomenclature[z,02]{UE}{User equipment}

  %first letter X is for Other Symbols

\nomenclature[x,00]{$\forall$}{For all} 
\nomenclature[x,12]{$\lfloor x \rceil$}{$x$ is rounded to the nearest integer value} 
\nomenclature[x,13]{$\lfloor x \rfloor$}{$x$ is rounded down to the nearest integer value} 
\nomenclature[x,20]{$\mathbb{N}$}{Set of natural numbers} 
\nomenclature[x,21]{$\mathbb{R}$}{Set of real numbers}
\nomenclature[x,21]{$\mathbb{Z}$}{Set of integer numbers}
\nomenclature[x,30]{$\mathbb{P}(X=x)$}{Probability that the random variable $X$ is equal to $x$}
\nomenclature[x,31]{$\mathbb{P}(X\geq x)$}{Probability that the random variable $X$ is not less than the value $x$} 
\nomenclature[x,32]{$X:=\mathrm{PD}(\lambda)$}{$X$ is a Poisson distributed random variable with density parameter $\lambda$ }%\nomunit{[$\lambda \in \mathbb{R}^+$]}
\nomenclature[x,40]{$G<<C$}{Energy generation of PV cell/cells is significantly smaller than energy consumption of BS} 
\nomenclature[x,41]{$G<C$}{Energy generation of PV cell/cells is slightly smaller than energy consumption of BS} 
\nomenclature[x,42]{$G>C$}{Energy generation of PV cell/cells is slightly greater than energy consumption of BS} 
\nomenclature[x,43]{$G>>C$}{Energy generation of PV cell/cells is significantly greater than energy consumption of BS} 
\nomenclature[x,70]{$\lvert \lvert BS_i - BS_j \rvert \rvert$}{Euclidean distance between $BS_i$ and $BS_j$}% \nomunit{[m]} 
\nomenclature[x,90]{$(i,j)$}{Directed edge from $BS_i$ to $BS_j$} 
\nomenclature[x,01]{$n%! $}{Factorial of non-negative integer $n$, $n \in \mathbb{N}_0$}
  




 