 \clearpage
\addcontentsline{toc}{chapter}{List of Publications}

\begin{center}
\Huge\textbf{{List of Publications}}
\end{center}


\vspace{\baselineskip}
\textbf{Published journal papers:}

 \cite{8491374} \textbf{D. Benda}, X. Chu, S. Sun, T. Q. S. Quek, and A. Buckley, “Renewable energy sharing among base stations as a min-cost-max-flow optimization problem,” \textit{IEEE Transactions on Green Communications and Networking}, vol. 3, no. 1, pp. 67–78, March 2019.

 \cite{my} \textbf{D. Benda}, S. Sun, X. Chu, T. Q. S. Quek, and A. Buckley, “PV cell angle optimization for energy generation-consumption matching in a solar powered cellular network,” \textit{IEEE Transactions on Green Communications and Networking}, vol. 2, no. 1, pp. 40–48, March 2018.

\vspace{\baselineskip}
\textbf{Published conference papers:}

\cite{APWCS} \textbf{D. Benda}, X. Chu, S. Sun, T. Q. S. Quek, and A. Buckley, “Optimal clustering of energy-harvesting base stations,” \textit{in Proc. IEEE VTS APWCS}, Hsinchu, Taiwan, Aug 2018.  

  \cite{my_con3} \textbf{D. Benda}, X. Chu, S. Sun, T. Q. S. Quek, and A. Buckley, “Modeling and optimization of energy sharing among base stations as a minimum-cost-maximum-flow problem,” \textit{in Proc. IEEE VTC-Spring}, Porto, Portugal, Jun 2018.
	
 \cite{my2} \textbf{D. Benda}, X. Chu, S. Sun, T. Q. S. Quek, and A. Buckley, “PV cell orientation angle optimization for a solar energy harvesting base station,” \textit{in Proc. IEEE GLOBECOM}, Singapore, Dec 2017.

 \cite{my4} \textbf{D. Benda}, X. Chu, S. Sun, T. Q. S. Quek, and A. Buckley, “PV cell angle optimisation for energy arrival-consumption matching in a solar energy harvesting cellular network,” \textit{in Proc. IEEE ICC}, Paris, France, May 2017.


\vspace{\baselineskip}
\vspace{4cm}
\textbf{Accepted journal paper for publication (not published yet):}

 \cite{sub} \textbf{D. Benda}, S. Sun, X. Chu, T. Q. S. Quek, and A. Buckley, “PV cell orientation angles optimization for a base station equipped with several PV cells”, submitted to \textit{IEEE Transactions on Green Communications and Networking}

\vspace{\baselineskip}
\textbf{Accepted conference paper for publication (not published yet):}

\cite{sub2} \textbf{D. Benda}, S. Sun, X. Chu, T. Q. S. Quek, and A. Buckley, “Optimal deployment of energy harvesters with anti-correlated energy generation
at base stations”, submitted to \textit{ICC 2020}
